### 2016-08-04 rebuttal.tex

\documentclass[answers,12pt]{exam}
\usepackage{xcolor}

\unframedsolutions
\shadedsolutions
\renewcommand{\solutiontitle}{}

\begin{document}

Dear Editor, \bigskip

Please read below our answer about the
questions made by you and reviewers. I hope that you agree
with all our comments. \bigskip

Best regards,\bigskip

The authors

\pagebreak

\section{Editor}

\begin{questions}
\question Spell foo as bar
\begin{solution}
 We opted to follow the ABC style of ...
\end{solution}
\question  Include reference to Really, Important and Stuff (2010)
\begin{solution}
Section 2 has been updated and the discussion ...
\end{solution}
\end{questions}

\section{Reviewer 1}

\begin{questions}
\question one
\begin{solution}
 We opted to follow the ABC style of ...
\end{solution}
\question  two
\begin{solution}
Section 2 has been updated and the discussion ...
\end{solution}
\end{questions}

\section{Reviewer 2}

\begin{questions}
\question one
\begin{solution}
 We opted to follow the ABC style of ...
\end{solution}
\question  two
\begin{solution}
Section 2 has been updated and the discussion ...
\end{solution}
\end{questions}

\section{Reviewer 3}

\begin{questions}
\question one
\begin{solution}
 We opted to follow the ABC style of ...
\end{solution}
\question  two
\begin{solution}
Section 2 has been updated and the discussion ...
\end{solution}
\end{questions}

\end{document}

### 2016-08-04 architecture.tex
Clarify commutative assumption
This is point 1 of the reviewer 1.

Now it should be clear, that symbols assumed
to be commutative, unless _both_ specified to
be non-commutative.

Not sure how much else we should add about the
rest of this point.  I.e. how to declare commutators.

Some of the common assumptions that SymPy allows are \texttt{positive},
\texttt{negative}, \texttt{real}, \texttt{nonpositive}, \texttt{integer},
\texttt{prime} and \texttt{commutative}.\footnote{If $A$ and
$B$ are Symbols created with \texttt{commutative=False} then SymPy will keep
$A\cdot B$ and $B\cdot A$ distinct.} Assumptions on any object can be checked with the
\verb|is_|\texttt{\textit{assumption}} attributes, like \verb|t.is_positive|.

@@

The assumptions system additionally has deductive capabilities. The
assumptions use a three-valued logic using the Python built in objects
\texttt{True}, \texttt{False}, and \texttt{None}.  Note that \texttt{False}
is returned if the SymPy object doesn't or can't have the assumption.
For example, both \texttt{I.is\_real} and \texttt{I.is\_prime} return
\texttt{False} for the imaginary unit \texttt{I}.

>>>>

Some of the common assumptions that SymPy allows are \texttt{positive},
\texttt{negative}, \texttt{real}, \texttt{nonpositive}, \texttt{integer},
\texttt{prime} and \texttt{commutative}. Assumptions on any object can
be checked with the \verb|is_|\texttt{\textit{assumption}} attributes,
like \verb|t.is_positive|.

@@

The assumptions system additionally has deductive capabilities. The
assumptions use a three-valued logic using the Python built in objects
\texttt{True}, \texttt{False}, and \texttt{None}.\footnote{Special
case is the \texttt{commutative} assumption: it can't be \texttt{None}.
Unless a Symbol is created with \texttt{commutative=False}, it's
assumed to commute with any other object with respect
to the multiplication operation.} Note that \texttt{False}
is returned if the SymPy object doesn't or can't have the assumption.
For example, both \texttt{I.is\_real} and \texttt{I.is\_prime} return
\texttt{False} for the imaginary unit \texttt{I}.
